%-------------------------
% Resume - January 2026
%-------------------------

\documentclass[11pt,letterpaper]{article}
\usepackage[margin=1in]{geometry}
\usepackage{fontspec}
\setmainfont{SF Pro Text}[
  BoldFont={SF Pro Text Bold},
  ItalicFont={SF Pro Text Italic}
]
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{changepage}
\usepackage{setspace}
\usepackage{fancyhdr}
\usepackage{lastpage}
\setstretch{1.2}
\setlist[itemize]{nosep, leftmargin=1em}

% Footer with page numbers and date
\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\fancyfoot[L]{Page \thepage\ of \pageref{LastPage}}
\fancyfoot[R]{Jan 27 2026}

% Section formatting
\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{12pt}{6pt}

% No paragraph indent
\setlength{\parindent}{0pt}

% Left-aligned text (no justification)
\raggedright

\begin{document}

%----------HEADER----------
{\Huge\bfseries Michael Vincent}\\[4pt]
\textit{Software Engineer, Full Stack, Payments \& Infrastructure} \\
Los Angeles, CA \\
https://mikevincent.dev

\vspace{8pt}

%----------EDUCATION----------
\section{Education}

\textbf{University of Texas at Tyler} \\
Master of Science, Industrial Engineering, 2015

\vspace{6pt}

\textbf{The Pennsylvania State University} \\
Bachelor of Science, Linguistics, 2011

\vspace{6pt}

\textbf{The Pennsylvania State University} \\
Bachelor of Arts, Journalism, 2011

%----------EXPERIENCE----------
\section{Experience}

\textbf{Senior Software Engineer, Payments Infrastructure} | \textbf{PricewaterhouseCoopers (PwC)} \\
September 2024 to Present | Los Angeles, CA \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Founding engineer for "Capital One Databolt," a vaultless tokenization platform for payment and financial services providers.
\begin{itemize}
  \item Wrote Go APIs for licensing, authentication, and partner onboarding.
  \item Deployed with Docker and Helm to AWS EKS and Azure AKS.
  \item Built field-level masking, tokenization, and encryption.
  \item Automated Kubernetes with Terraform, Istio, and cert-manager.
  \item Added OpenTelemetry tracing; Zelle signed as first customer.
\end{itemize}
\end{adjustwidth}

\vspace{24pt}

\textbf{Software Engineering Manager, Infrastructure} | \textbf{Cubic Transportation Systems} \\
October 2021 to April 2024 | San Diego, CA \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Led a global team shipping fare systems for DC Metro, NYC MTA, BART, LA Metro, and Boston MBTA.
\begin{itemize}
  \item Built cloud infrastructure with Terraform, AWS, and GitHub Actions.
  \item Won multiple company awards for engineering excellence.
  \item Deployed mTLS security with Istio on Kubernetes.
\end{itemize}
\end{adjustwidth}

\vspace{24pt}

\textbf{Lead Senior Software Engineer, Infrastructure} | \textbf{Cubic Transportation Systems} \\
October 2019 to October 2021 | San Diego, CA \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Built the "Cubic AI Chatbot" letting riders check card balances by phone and text, plus ML pipelines for fare optimization.
\begin{itemize}
  \item Deployed chatbot on Azure with natural language processing.
  \item Built CI/CD for 20 Java apps with Jenkins, Docker, Helm, Vault, and Terraform.
  \item Built serverless pipelines with AWS Lambda and Azure Functions.
\end{itemize}
\end{adjustwidth}

\vspace{24pt}

\textbf{Senior Software Engineer, Infrastructure} | \textbf{Cubic Transportation Systems} \\
May 2017 to October 2019 | Washington, DC \\[2pt]
\begin{adjustwidth}{1em}{0pt}
First DevOps hire. Transformed legacy infrastructure to containers and cloud for fare systems serving 10M+ daily riders.
\begin{itemize}
  \item Introduced Terraform, Kubernetes, and Docker to the organization.
  \item Built CI/CD for embedded fare devices with Jenkins and Wind River Linux.
  \item Passed PCI, SOC2, ISO, and SOX audits.
  \item Built Kubernetes monitoring with Prometheus and Grafana.
\end{itemize}
\end{adjustwidth}

\vspace{24pt}

\textbf{Senior Software Engineer, Infrastructure} | \textbf{EPAM Systems} \\
May 2016 to April 2017 | Washington, DC \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Promoted to senior backend engineer at digital UX agency building apps for enterprise clients.
\begin{itemize}
  \item Built Fannie Mae web app for mortgage lenders.
  \item Built Lockheed Martin Intranet on headless Drupal.
  \item Built NY Fashion Week 2015 mobile app.
  \item Wrote PostgreSQL migrations with Liquibase.
  \item Deployed microservices with Docker and Kubernetes 1.2.
\end{itemize}
\end{adjustwidth}

\vspace{24pt}

\textbf{Software Engineer, Infrastructure} | \textbf{EPAM Systems} \\
May 2015 to April 2016 | Washington, DC \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Backend engineer on full-stack team at digital UX agency building mobile apps and e-commerce platforms.
\begin{itemize}
  \item Built Poison Control mobile app.
  \item Built Canadian Tire e-commerce store.
  \item Built U.S. Conference of Catholic Bishops mobile app.
  \item Moved PostgreSQL database to multi-tenant setup with zero downtime.
  \item Worked with Docker, Ansible, Jenkins, VMware ESXi, Ubuntu, CentOS, and Cisco ASA firewalls.
\end{itemize}
\end{adjustwidth}

%----------PROJECTS----------
\section{Projects}

\textbf{Io Pictures Corporation} \\
January 2022 to Present | Los Angeles, CA \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Founded California C Corporation engaged in buying, selling, and distributing licensed and acquired motion picture titles.
\begin{itemize}
  \item Sold rights to Tubi, Amazon, Apple, and Google through professional contacts.
  \item Negotiated domestic, international, publicity, and all-rights deals.
  \item Built digital distribution pipeline.
\end{itemize}
\end{adjustwidth}

\vspace{24pt}

\textbf{The Archive of American Radio, Inc.} \\
June 2025 to Present | Los Angeles, CA \\[2pt]
\begin{adjustwidth}{1em}{0pt}
Founded 501(c)(3) tax-exempt nonprofit preserving American radio drama. Developers of the "Anthology" mobile app for listening to public-domain audio.
\begin{itemize}
  \item Built data processing pipelines and Cloudflare Workers APIs.
  \item Used Cloudflare D1, R2, Turso, Supabase, and Vercel.
  \item Developed custom OpenAI models for metadata extraction and search.
\end{itemize}
\end{adjustwidth}

%----------SKILLS----------
\section{Skills}

\textbf{Languages:} Go, Python, JavaScript/TypeScript, Java, SQL, Bash, Rust \\
\textbf{Cloud:} AWS, Azure, Google Cloud Platform \\
\textbf{Compute:} Kubernetes, Docker, AWS EKS, Azure AKS, AWS Lambda, Azure Functions, GCP GKE \\
\textbf{Storage:} AWS S3, Cloudflare R2, Azure Blob, Redis, Kafka \\
\textbf{Network:} Istio, cert-manager, mTLS, Cloudflare Workers, API Gateway, Load Balancing \\
\textbf{Databases:} PostgreSQL, MySQL, MongoDB, Turso, Cloudflare D1, Supabase, DynamoDB \\
\textbf{Infrastructure:} Terraform, Helm, GitHub Actions, Jenkins, ArgoCD, Pulumi \\
\textbf{AI/ML:} OpenAI API, LangChain, Vector Databases, RAG, Embeddings \\
\textbf{Observability:} Prometheus, Grafana, OpenTelemetry, Datadog, PagerDuty \\
\textbf{Security:} Vault, OAuth2, JWT, PCI-DSS, SOC2, Zero Trust

\end{document}
